|

### 2021-05-26 article/article.Rmd
changes to methods section and intro

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Most
early studies that empirically tested the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and different measures of government spending, although the
effect was often limited to one house [e.g., @baqir2002districting;
@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
questioned the validity of the "law of $1/n$". For instance, spending limits,
bicameralism, or strong executives may reduce the inefficiency of pork barrel
projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Given this diversity of empirical
findings, a systematic review of the existing evidence may help us reach a
meaningful conclusion about the effect of legislature size on public spending.
Meta-analysis is the most appropriate method for this task. Meta-analysis
combines the outcomes of multiple studies into a single estimation and allows
scholars to draw robust conclusions from the aggregated data
[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
report separate estimates for the impact of lower and upper house size on 
government expenditures. In the full model, we add every outcome reported in the 
papers, regardless of whether the coefficient comes from the main tables or from 
robustness checks. We discuss our sampling process in the Methods section and in 
the Supplementary Material.}
Our independent variables consist of three measures, namely the size of the
lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
in the upper chamber ($k$). We evaluate their effect upon public expenditure per
capita, the natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. We then estimate if the results vary
according to four potential sources of effect heterogeneity.

Aggregate results show that legislative size has no significant impact on
public spending. However, the meta-regressions suggest that our study sample
has high levels of heterogeneity, and effects differ substantially according to
study specifications. We find that one reliable predictor of effect size is the
research method employed in the original paper. While papers that employ
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".
Additionally, we find that non-majoritarian voting systems decrease government
spending as a percentage of GDP, which is also evidence against the theoretical
expectations of the "law of $1/n$", and they do not have a relevant impact on
the other measures of public expenditure. In summary, our analysis does not
provide robust support for the theory as originally conceived, and causal
inference models suggest that larger legislatures are associated with lower
public spending.

@@

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in the
English language, and to make our study sample comparable, we only selected
papers that use quantitative methods to analyse data\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables. Please refer to Section C in the Supplementary Material for a
detailed description of the selection procedure. We also included two PRISMA
(Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow
diagrammes \citep{liberati2009prisma} showing the number of resulting papers
after each review step.}. After this stage, we identified the variables that
authors employ more often to measure government expenditure and legislature
size, our dependent and independent variables, respectively. For government
expenditure, our study sample uses (i) public expenditure as a share of GDP;
(ii) public expenditure per capita; and (iii) the natural logarithm of public
expenditure per capita as its main variables of interest. In regards to
legislature size, the variables are (i) lower chamber size; (ii) natural
logarithm of lower chamber size; and (iii) upper house size\footnote{There are
a few important nuances concerning coding of these variables. For instance,
unicameralism is captured both by lower chamber size ($n = 7$) and by log lower
chamber size ($n = 5$). Since much of the literature estimates how
institutional designs affect this relationship, ours and many other articles
use both lower and upper chamber sizes as main explanatory variables. We did
not find any articles that used the natural logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. In the third
search round, we looked into the personal webpages of every author we had
already included in our previous sample. The purpose of this manual search was
to assess whether there was any working paper or unpublished manuscript which
we might had missed in the previous queries. All papers we found in the last
search had already been included in our sample. Combined, the three searches
produced a dataset of `r length(unique(dat$id))` studies as of the
10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
list of articles we analyse in this paper.

@@

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables of interest are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
included only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets in their analyses,
and almost all papers fit more than one model with similar variables, what
suggests that the assumption does not hold. We use two procedures to tackle this
problem. First, we created two sets of study coefficients to reduce the impact
of multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
articles analysed two dependent or independent variables of
interest\footnote{The papers that used more than one dependent or independent
variable of interest are \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are very similar when we use the extended
set.

@@

In this letter, we assess the empirical validity of the "law of $1/n$". Based
on a sample of `r length(unique(dat$id))` publications on the topic, our
meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. If such
effect exists, it is likely driven by an increase in $k$, the size of the upper
legislature, as suggested by several studies in the literature
[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
@chen_malhotra_2007; @gilligan2001fiscal; @primo2006stop]. Instead, we find
better evidence for the "reverse law of $1/n$", which posits that larger
legislatures lead to lower government spending. This is mainly because studies
using regression discontinuity designs, a method that has robust internal
validity, consistently indicate a negative relationship between lower house size
and the logarithm of expenditure per capita [@hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size].

@@

Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
plausible reason may be that there are few incentives for the pure accumulation
of knowledge in the social sciences, at least when compared to the benefits
scholars may accrue when they challenge or add features to existing theories
[@geddes2003paradigms]. This leads to a reduced number of replication studies in
the field, although we have seen some positive changes in this respect, such as
EGAP's _Metaketa Initiative_.\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.} For instance, in our sample, papers added supermajority rules
[@lee2015supermajority; @lee2016supermajority], redistricting
[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
bicameralism [@ricciuti2004legislature], and the interplay between upper and
lower houses [@chen_malhotra_2007] to the main theory, but a comprehensive
procedural replication of the findings using different samples is yet to be
written. The addition of new features has the benefit of enriching the original
theory with useful details, although it has the disadvantage of not providing a
conclusive test to the "law of $1/n$".

>>>>

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. Early
studies that empirically tested the "law of $1/n$", as the theory is currently
known, indeed found a positive correlation between the number of legislature
seats and different measures of government spending, although their results
were mainly based on US state legislatures and the effect was often limited to
one house [e.g., @baqir2002districting; @gilligan1995deviations;
@gilligan2001fiscal].

Later research, however, has questioned the validity of the "law of $1/n$".
@primo2008distributive affirm that, due to spatial spillovers, a collection of
small districts can supply public goods more efficiently than the central
government. The authors conclude that a "reverse law of $1/n$" may hold,
wherein a higher number of legislators in small constituencies decrease the
overall public spending. Similarly, @primo2006stop and @chen2007law find that
lower and upper chambers may have mixed effects on government spending, while
@petterssonlidbom2012size argues that the impact of larger chamber sizes is
negative when using data from Finland and Sweden.

Since the wide range of empirical tests of the "law of $1/n$" has produced
conflicting results, scholars have expanded this research agenda and
investigated how institutional factors condition the original formulation of
the theory. For instance, authors such as @crowley2019law and
@pecorino2018supermajority accurately point out that collective action problems
have been overlooked in the literature, and recent findings indicate that
bicameralism [@maldonado2013legislatures], intergovernmental competition
[@crowley2015local], redistricting [@lee2018court], and party ideology
[@bjedov2014impact] strongly influence the relationship between seats and
spending. Moreover,

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We select `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. Out 
of the `r dim(dat)[1]` coefficients
included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
negative and statistically significant. Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
sources of study heterogeneity, enabling researchers to assess threats to
external validity and direct future efforts into more promising areas of
academic inquiry [@doucouliagos2008democracy].

We believe the scrutiny of the law expanded its initial scope in two directions. One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards. They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S. majoritarian local legislatures, for which the law was conceived. Another sector of the scholarship overrides this institutional context. They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc. produce more nuanced results. For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative. While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness. We address all of these developments in this study. We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.

Aggregate results show that legislative size has no significant impact on
public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications. In the broadest aggregation models, unicameralism supports the positive effect predicted by the 
law of $1/n$. Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework. It also indirectly endorses studies that find odd results in bicameralism. As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal]. 
Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.

The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods. While papers that employ conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies using modern methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
with previous findings that lend partial support to the law of $1/n$ 
[@chen2007law; @crowley2015local; @primo2006stop]. An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results. Overall, our analysis does not
provide robust support for the theory as originally conceived.

@@

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that were published in English and
cited \citet{weingast1981political}, as it is the foundational work in the
literature on the "law of $1/n$". To ensure that our sample was comparable, we
only selected papers that used quantitative methods to analyse
data\footnote{Since meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our selected variables. Please refer to Section C in the Supplementary Material
for a detailed description of the selection procedure. We also included two
PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
flow diagrammes \citep{liberati2009prisma} showing the number of resulting
papers after each review step.}. After this stage, we identified six
measurements that the literature often employs to quantify government
expenditure and legislature size. For government expenditure, our study sample
uses (i) public expenditure as a share of GDP; (ii) public expenditure per
capita; and (iii) the natural logarithm of public expenditure per capita as its
main variables of interest. In regards to legislature size, the variables are
(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
upper house size\footnote{There are a few important nuances concerning coding
of these variables. Unicameralism, for example, is captured both by lower
chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
the literature estimates how institutional designs affect this relationship,
ours and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any article that used the natural
logarithm of upper chamber size in their models.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. This search
added two new results to our sample (**CITE**), but neither of them included
variables beyond the six measures we had previously identified. In the third
search round, we looked into the personal webpages of every author whom we had
already included in our sample. The purpose of this manual search was to assess
whether there was any working paper or unpublished manuscript that we had
missed in the two former queries. All papers we found in the last search had
already been included in our sample. Combined, the three searches produced a
dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th}
of March 2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

@@

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`). 
These six variables formed a $3 \times 3$ table, yet not all combinations were
available in the data. We found no studies that correlate public expenditure
per capita with either upper chamber size or the natural logarithm of lower
house size. Thus, our meta-analysis contains seven of the nine possible
variable combinations.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive statistics of moderators",
          format  = "latex")
```
\normalsize

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
added only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets in their models,
and almost all papers fit more than one regression with similar variables, what
suggests that the assumption above does not hold. We use two procedures to tackle this
problem. First, we created two sets of study coefficients to reduce the impact
of multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
articles analysed two dependent or independent variables of
interest\footnote{The papers that used more than one dependent or independent
variable of interest are \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are very similar when we use the extended
set.

@@

In this letter, we assess the empirical validity of the "law of $1/n$". Based
on a sample of `r length(unique(dat$id))` publications on the topic, our
meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. If such
effect exists, it is likely driven by an increase in $k$, the size of the upper
legislature, as suggested by several studies in the literature
[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
better evidence for the "reverse law of $1/n$", which posits that larger
legislatures lead to lower government spending. This is mainly because studies
using regression discontinuity designs, a method that has robust internal
validity, consistently indicate a negative relationship between lower house size
and the logarithm of expenditure per capita [@hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size].

@@

Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
plausible reason may be that there are few incentives for the pure accumulation
of knowledge in the social sciences, at least when compared to the benefits
scholars may accrue when they challenge or add features to existing theories
[@geddes2003paradigms]. This leads to a reduced number of replication studies in
the field, although we have seen some positive changes in this respect, such as
EGAP's _Metaketa Initiative_.\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.} For instance, in our sample, papers added supermajority rules
[@lee2015supermajority; @lee2016supermajority], redistricting
[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
bicameralism [@ricciuti2004legislature], and the interplay between upper and
lower houses [@chen2007law] to the main theory, but a comprehensive
procedural replication of the findings using different samples is yet to be
written. The addition of new features has the benefit of enriching the original
theory with useful details, although it has the disadvantage of not providing a
conclusive test to the "law of $1/n$".
